Examining the Flu through wILI

### 2020-10-08 dev/flu_analysis.Rmd

```{r season-df_vis, echo = F}
start_year = 1999
end_year = 2017
flu_season_info_df <- data.frame(year = start_year:end_year) %>%
  mutate(start_date = paste0(as.character(year), "-10-01"),
         end_date = paste0(as.character(year+1), "-08-30"),
         even_year = c( "odd", "even")[(year %% 2) + 1]) %>%
  mutate(start_date = as.Date(start_date, format= "%Y-%m-%d"),
         end_date = as.Date(end_date, format= "%Y-%m-%d"))
```

>>>>

```{r season-df_vis, echo = F}
start_year = 1999
end_year = 2017
flu_season_info_df <- data.frame(year = start_year:end_year) %>%
  mutate(start_date = paste0(as.character(year), "-09-16"), # splitting september equally
         end_date = paste0(as.character(year+1), "-09-15"),
         even_year = c( "odd", "even")[(year %% 2) + 1]) %>%
  mutate(start_date = as.Date(start_date, format= "%Y-%m-%d"),
         end_date = as.Date(end_date, format= "%Y-%m-%d"))
```
